Persistence of marine populations under climate and fishing

### 2014-02-20 Writing/MS.tex
proofreading;

\noindent Regardless of the exact functional form of the recruitment function, the critical parameter in determining population persistence is how quickly recruitment increases when the population 
size is near (but above) $0$, which is equivalent to the intrinsic growth rate, $R_0=f'(0)$.  Analyzing this kind of model becomes easier if the dispersal kernel is separable into its dependence on the source of larvae and its dependence on the destination of the larvae, i.e.~if there are functions $a_i, b_i$ such that $k(x- y) = \sum^\infty_{i=1} a_i(x)b_i(y)$ and we use such a kernel in our analytical expressions.

@@

We would like to know the rate of environmental shift and the harvesting rate such that  the population will be able to persist as long as the 
environment moves more slowly or we harvest less severely than those parameters. We call these, respectively, the critical rate of environmental shift, $c^*$, and the critical harvesting rate, $h^*$. 
We found these rates by finding the parameters that make the trivial pulse unstable.   In our analyses, as in \citep{Latore:1998fk}, we used the separable Gaussian kernel given by

For each kernel, the population's ability to persist depends on properties of the population itself-- the expected distance a larva disperses ($\langle d \rangle$) and the intrinsic growth rate ($R_0$); properties of the environment-- the length of the viable patch ($L$) and how quickly the environment is shifting ($c$); and the harvesting rate ($h
$).  The population biomass at equilibrium depends on the function form of recruitment, but population persistence only depends on the intrinsic growth rate $R_0$.  If the environment shifts more quickly than the critical rate $c^*$ or the population is harvested at more than the critical rate $h^*$ then the population will not be able to persist, as described in the Appendix.  For a Gaussian kernel, the critical rates $c^*$ and $h^*$ are those values of $c$ and $h$ such that

>>>>

\noindent Regardless of the exact functional form of the recruitment function, the critical parameter in determining population persistence is how quickly recruitment increases when the population 
size is near (but above) $0$, which is equivalent to the intrinsic growth rate, $R_0=f'(0)$.  Analyzing this kind of model becomes easier if the dispersal kernel is separable into its dependence on the source of larvae and its dependence on the destination of the larvae, i.e.~if there are functions $a_i, b_i$ such that $k(x- y) = \sum^\infty_{i=1} a_i(x)b_i(y)$.  In our analyses, as in \citep{Latore:1998fk}, we used the separable Gaussian kernel given by

@@

If the population is harvested at low enough levels and the environment shifts slowly enough, the population will be able to persist.  There are threshold values of the harvesting rate $h$ and the rate of environmental shift $c$ such that if the parameters are increased beyond these values, the population will be driven extinct.  We found these critical parameters, $h^*$, and  $c^*$, by finding the parameters that make the trivial pulse unstable.   Details are provided in Appendix \ref{stab}.

For each kernel, the population's ability to persist depends on properties of the population itself-- the expected distance a larva disperses ($\langle d \rangle$) and the intrinsic growth rate ($R_0$); properties of the environment-- the length of the viable patch ($L$) and how quickly the environment is shifting ($c$); and the harvesting rate ($h
$).  The population biomass at equilibrium depends on the function form of recruitment, but population persistence only depends on the intrinsic growth rate $R_0$.  For a Gaussian kernel, the critical rates $c^*$ and $h^*$ are those values of $c$ and $h$ such that
